\documentclass[11pt,]{moderncv}
\moderncvtheme[blue]{classic}
\usepackage{fontawesome}
% \usepackage{setspace}
\usepackage[utf8]{inputenc}
\usepackage[top=1.1cm, bottom=1.1cm, left=2cm, right=2cm]{geometry}
\setlength{\hintscolumnwidth}{2.5cm}

\firstname{Ruben}
\familyname{Fiszel}
\title{SWE at Palantir\newline{}\newline{}Functional Programming, Compilers, ML \newline{}and Distributed Systems}
\phone{(415) 570-4109}
\email{rubenfiszel@gmail.com}
\extrainfo{\faGithub ~ rubenfiszel \\ \faLinkedin ~ rubenfiszel \\ \faGlobe rubenfiszel.github.io}


\begin{document}
\maketitle

\section{Work Experience}
\cventry{2017 - Present}{Palantir}{\normalsize{\textbf{Software Engineer}}}{London, UK}{}{
\textbf{Core distributed infrastructure:} refactored the microservice webserver library, switching it from Jetty to Undertow, as well as developing meta-programming generators targeting it. Resulted in large performance, correctness, and maintainability improvements.
\\ \textbf{SQL Language Server}: Developed SQL Analysers and an infrastructure compatible with the Language Server Protocol to provide live feedback to users on our internal web IDE.
\\ \textbf{Devtools}: Developed Gradle plugins to solve our ``Dependency hell'' situation.}
\cventry{Summer 2016}{Skymind}{\normalsize{\textbf{Software Engineer Intern}}}{San Francisco, US}{}{ Wrote deeplearning4j's official Deep Reinforcement Learning library RL4J (github.com/deeplearning4j/rl4j).}
\cventry{Summer 2013}{Crossing-Tech}{\normalsize{\textbf{Software Engineer Intern}}}{Lausanne, Switzerland}{}{NLP prototyping.}


\section{Education}
\cventry{2017}{Stanford University}{Visiting Student Researcher}{}{}{Master thesis on ``abstraction without compromise'' at the DAWN lab under Prof. Kunle Olukotun and Prof. Martin Odersky supervision. Contributed to Spatial, a Scala to Hardware (FPGA) compiler and developed autonomous driving of drones using Rao-Blackwellized Particle Filters.}
\cventry{2017}{École Polytechnique Fédérale de Lausanne (EPFL)}{MSc in CS}{}{}{MSc in \textbf{Computer Science} with a minor in \textbf{Financial Engineering}
\\ \textbf{Overall GPA: 5.58/6 (Top 5\%)}}
\cventry{2015}{Johns Hopkins University}{Bachelor student in exchange}{}{}{Third and Last year of Bachelor: Study abroad. \textbf{Selected with a scholarship}}
\cventry{2015}{École Polytechnique Fédérale de Lausanne (EPFL)}{BSc in CS}{}{}{
\textbf{Overall GPA: 5.16/6 (Top 5\%)}}


\section{Relevant Projects}
\cventry{2018}{Paper: Spatial: A Language and Compiler for
Application Accelerators}{6th Author}{}{}{PLDI2018 https://doi.org/10.1145/3192366.3192379}
\cventry{2016}{Study of deep reinforcement learning methods and deep exploration}{}{}{}{Semester project at the Laboratory of Artificial Intelligence at EPFL}

\section{Skills}
\cvitem{Programming}{Scala, Java, Python, Haskell, Typescript, OCaml, Erlang}
\cvitem{Interests}{Statistics, High-Performance Computing, Compilers, Functional Programming, Machine Learning, NLP, Distributed Systems (in particular Actor Frameworks)}
\cvitem{Programming Contests}{
  TreeHacks 2017 ~ HackEPFL 2016 ~ HopHacks 2015 ~ Google Code Jam: 2012, 2013 ~ Helvetic Coding Contest (hc2): 2013 ~ IEEEXtreme Programming: 2013 (72nd Mondial Ranking) ~~Prologin: 2012, 2011
}
\cvitem{Others}{Elected class president throughout all my years at EPFL, Ski instructor, Teaching Assistant in various courses at EPFL}

\end{document}
